Working title: the most amaz-zing SPIM and how we built it.

### 2015-01-20 latex-style-files-spie-manuscript/manuscript1.0.tex

Here we will describe a state-of-the-art LSFM, as it is implemented in our lab, which can be used to acquire 3D data sets of clarified mouse brains. The LSFM features double-sided illumination with a digitally scanned light sheet and a sample chamber which has been specifically designed for the the imaging of large ($> 1cm^3$), immersed and freely movable samples. After briefly presenting the optical clearing protocol we employ to render our samples transparent, we explain how to prepare and mount the samples for stable, 3D imaging for several days. In addition to a detailed description of all opto-mechanical components, we further present a practical guide for the alignment of a LSFM, a non-trivial task whichhas too often been summarised in a single sentence. A systematic approach to handle, store and analyse the data is also given. We further explain about the data volume we produce how it can be reduced and handled. We finish with some nice data and an outlook.  The final sentence of the introduction needs to be amazing.

\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{PanelSampel.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:Panel0} (A) Schematic of light sheet microscopy.  Excitation and detection occur on independent perpendicular axes. (B) Mounting of a claried brain. The brain is glued onto a coverslip and inserted into an adapter that slides into a Teflon cylinder.} 
   \end{figure}

\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{Panel1.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:Panel1} Schematic of light sheet microscopy. (A) Fluorescence excitation (along x axis) and detection (along z axis) are operated on independent, perpendicular light paths where the excitation light sheet and the detection focal plane overlap. The clarified, fluorescently-labelled brain (B) is mounted on a Teflon cylinder inside the watertight chamber (D) and can be translated and rotated freely with piezo motors (D). The sample is glued onto a cover slip which is slid into a custom made adapter mount that is inserted into the Teflon cylinder (E).} 
   \end{figure}

\section{Optical clearing and sample mounting}
%Biological tissue is, bar of very few exemptions like the cornea or zebrafish larvae, highly scattering. Scattering is the deflection of light rays due to the heterogeneous mixture of cells and sub-cellular structures with varying refractive indices. Rayleigh scattering, the nearly isotropic and strongly wavelength dependent scattering of light by particles much smaller than the wavelength of light, and Mie scattering, which occurs on cellular structures such as organelles and other refractive structures which are larger than the wavelength of light, far outweigh absorption and cause most biological tissues to be opaque. In the visible spectrum, the scattering of fluorescence photons is dominant over ballistic fluorescence such that for the imaging of large samples optical clearing methods based on refractive index matching have been employed. These methods involve several chemical sample preparation steps to generate transparent yet structurally and anatomically intact tissue.
%
%A successful optical clearing method not only renders the tissue transparent but also causes neither quenching of protein fluorescence nor tissue distortion and is compatible with repetitive immunostaining. A very promising method called CLARITY\cite{Chung2013,Tomer2014} transforms tissue into a nanoporous, hydrogel-hybridized, lipid-free form. Crucially for high through-put clearing and imaging of large samples, the protocol, however, is ideally also fast, easy and cheap. Our lab therefore development a versatile, simple, rapid and inexpensive clearing method based on a water-soluble agent, 2,2'-thiodiethanol (TDE) which in combination with CLARITY allows for the optical clearing of entire mouse brains or human biopsies. With this protocol (see [cite Irene] for a detailed description) a mouse brain (Figure\ref{fig:Panel1},B) takes 1 month to clear at a costs of \$XY.

To elucidate neuronal projections and functional connections in structurally intact tissue it is paramount to be able to image centimeter-sized, clarified samples, such as mouse brains, with high resolution in whole mount preparation. While promising clearing protocols are well documented in literature\cite{Chung2013,Tomer2014}, the question of sample preparation and mounting in light sheet microscopy is not trivial but requires novel approaches to such extent that it is becoming a separate field of research and very diverse strategies such as FEP tubes, 3D printed chambers and Quartz cuvettes have been reported\cite{Kaufmann2012,Pitrone2013,Olarte2012,Tomer2014}, however, these approaches are limited to much smaller sample volumes. The problem of sample mounting in light sheet microscope arises form the fact that optical access to the sample is required from 3-4 planar sides leaving only two opposing sides to insert, fix and move the sample (Figure\ref{fig:Panel1},A). Most commonly the vertical direction is chosen. Stable mounting is hereby a key concern as a whole brain tomography can require image acquisition in excess of 24 hours and the effects of gravity, tissue shrinking/expansion and evaporation of the clearing solution over such time spans might have to be considered.

We designed a cubic, water-tight sample chamber (Figure\ref{fig:Panel1},C) that allows access from all six sides while maintaining the 3D integrity of large, clarified and fluorescently-labelled mouse brains. A motorized x-, y-, z-, $\theta$-stage (three M-122.2DD and one M-116.DG, Physik Instrumente) allows free 3D motion and rotation of a Teflon cylinder which reaches into the centre of the chamber (Figure\ref{fig:Panel1},D). The clarified brains are fixed with super glue to a coverslip which is slid into a custom made adapter and tightened with a plastic-capped screw. The adaptor is then inserted into the Teflon cylinder (Figure\ref{fig:Panel1},E) with the coverslip being positioned on the far side of the detection objective. Three different slits in the adapter correspond to varying distances to the detection objective and give variability in sample thickness for example to allow also for the mounting of rat brain hemispheres. The clarified brains are imaged immersed in clearing solution composed of 63\% TDE in Phosphate buffered saline (PBS) and a refractive index of 1.45.

@@

The custom-made, confocal light sheet microscope is equipped with 5 linearly polarised, cw lasers for fluorescence excitation (Figure\ref{fig:excitation},A). The wavelengths were chosen to excite the most common fluorophores (see Table\ref{tab:optomechanics} for the manufacturer and specifications of opto-mechanical components). The laser light from each laser is first collimated and expanded with a telescope (f140, f200) and then combined into a common path with a beam steering mirror and a long-pass filter (Semrock, LaserMUX\texttrademark\ series). An acousto-optical tunable filter (AOTF) acts as fast ($\mu s$) electronically tunable filter which uses the acousto-optical interaction inside an anisotropic medium to select and transmit any combination of up to four of the laser lines. The radio-frequency applied on the AOTF transducer controls the wavelength being transmitted into the first order and the radio-frequency amplitude allows to adjust the transmitted light intensity. Due to the nonlinear response of the AOTF we measured the AOTF light transmittance for each wavelength as a function of radio frequency amplitude and determined a look-up table to linearise the output. The zero order light is blocked by an iris. An electro-optical laser modulator acts like a wave plate with electrically controlled retardation and rapidly rotates (few hundreds ns) the input polarisation of the excitation light by $90\degree$. The wavelength-dependent, high voltage that needs to be applied to the birefringent crystal inside the modulator to change the optical path length is provided by a two-step pre-amplification system. First, a low voltage, analog signal from the DAQ board is pre-amplified with custom made electronics and then fed into a commercial high voltage amplifier. A digital line is used to electronically control the frequency of the polarisation shift. After the laser modulator the excitation beam is further expanded by a factor of 2 (f100, f200) with two achromatic doublets.

From here on three different light paths can be chosen through flip mirrors. One light path option guides the light through an axicon (apex angle of $160\degree$) and an achromatic doublet (f50) to create a Bessel beam. The other two options create Gaussian beams of different beam diameter. This diameter variation translates to different fields of view later on in the detection path. The three options are recombined before a polarising beam splitter cube which splits the excitation light depending on its polarisation into one of the two excitation arms which are built to be identical. The beam is reduced with a telescope (f350, f200) whose telecentric plane coincides with the mirrored surface of a galvanometric scanner (galvo). The galvos are mounted on a custom made optical breadboard which features two circular holes to pass the periscopic beams and a large central cut-out for the sample chamber and motor stages. The light sheet is generated digitally by scanning the excitation beam with a sawtooth signal applied to the galvo. This generates perfectly incoherent illumination resulting in fewer artefacts.%cite{StelzerNatMeth2014}.

The scan mirror surface is reimaged with a telescope (f50, f100) onto the back aperture a long working distance, low magnification objective (Nikon, 10x 0.3NA WD 17.5mm). The two excitation objectives are designed for air immersion. A coverslip glued to the front housing edge serves the dual purpose of maintaining the first diffractive surface between the front optical element and the air and to protect the front lens elements from the organic solvent. The sample chamber is tightly bolted  to the optical breadboard while soft connections through silicone bellows allow for adjustive movements of the objectives and free 3D motion of the motor stages. All connections are sealed with rubber rings and silicone caulk and additionally tightened with cable binders. In this way the objectives can be refocused and realigned without compromising the watertight seal of the chamber.

@@

		Fluorescence is collected on a axis perpendicular to the excitation with an objective that was specifically designed for immersion in clearing solutions of various refractive indices. The objective is equipped with a correction collar allowing for immersion in media with refractive indices ranging from 1.41 to 1.52 (Olympus, XLSLPLN25XGMP). To image the whole volume of interest the objective has a relatively low magnification of 25x and a large working distance of 8mm yet a high numerical aperture (1.0NA) affords high resolution imaging. HERE WE'LL NEED SOME CHARACTERISATION DATA. An overview of imaging properties and derived quantities is given in Table\ref{tab:resolution}. We use a tube lens of 200mm to create an image on a sCMOS camera (Orca Flash4.0, Hamamatsu). A fluorescent filter is used to block out any excitation light. The camera chip of over 4 megapixels is read out in one sweep from top to bottom in the so-called light sheet mode in which only a subset of horizontal lines is exposed and consequently read out and any time. This sweeping line exposure creates a virtual confocal slit. Confocality is achieved by synchronising a single line which generates the light sheet with the exposure of a few lines on the CMOS chip.

%For image acquisition the sample is slowly translated at a fixed speed along the detection axis through the light sheet. Images are recorded at a frame rate of 44Hz in different planes along the optical axis of the detection lens (here z) to acquire a stack. After successful stack acquisition the sample is moved to an adjacent vertical position (here y) to acquire the next image stack. Once the entire vertical slice composed of z stacks is acquired the sample is moved to an incremented x position. In this way the entire cubic volume is imaged.

	\subsection{Alignment}

\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{Panel3.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:alignment} (A) Basic geometrical optics of a double-sided illumination light sheet microscope. AD: achromatic doublet, PBS: polarising beam splitter, red: objective back focal planes and conjugated telecentric planes, green: image planes, blue: 4f telecentric lens system. (B) The alignment mirror can be rotated to precisely reflect at $45\degree$. (C) With lateral movement the alignment mirror can be placed such that light is transmitted into the opposing excitation arm. (D) Alignment mirror with drilled hole for light transmission, mount for tip adjustment and adaptor for the Teflon tube.} 
   \end{figure}

For light sheet microscopy it is crucial that excitation and detection occur on perpendicular axes because any deviation from this geometry results in obscured images of reduced resolution and contrast. The objectives need to be perfectly confocal so that the fluorescence that is generated in the swept excitation beam also falls within the detection objective's depth of field. Telecentricity, that is the imaging with two lenses which are the sum of their focal lengths apart, has to be strictly observed in all three arms (Figure\ref{fig:alignment},A), which means the galvo scanners need to be precisely placed in telecentric planes of the excitation objectives while in the detection path, the camera chip needs to be positioned in an image plane of the detection objective. Additionally, homogeneous illumination from both sides impose strict symmetry considerations on both illumination arms that have not only to be sufficiently aligned within themselves respectively but function as pair with recursive dependence.

Our microscope was aligned with two tools, a shear plate to qualitatively assess collimation and a small mirror that can be mounted inside the sample chamber where the sample would usually be. The 0.5in mirror was first pierced with a drill using a ceramic drill bit to produce a hole roughly in its centre of the approximately the same diameter as the excitation beam inside the sample chamber. Using a compact single axis adjustable mirror mount (V50-AX, Newport) attached to the Teflon cylinder inside the chamber allows to to adjust the pitch of the reflection with the mount and the yaw with the rotation stage while at the same time providing a very space efficient mounting for the pierced 0.5in mirror. With this ``sample mirror" three different position can now be easily implemented, firstly, back reflection by hitting the reflective surface at $0\degree$, secondly, transmission by laterally displacing the mirror until the light passes through the drilled hole, and thirdly, reflection of the light by $90\degree$ by precisely turning the mirror mount by $45\degree$ using the rotation stage.

\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{Panel4.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:alignment2} (A) Working principle of a microscope objective (left): a collimated input beam in converted into a spherical wavefront. Right: inverted light path where a focal spot in the back aperture creates a collimated output. (B) Recursive placement of lenses using the sample mirror in back-reflection mode, (C) in transmission mode and (D) in reflection mode.} 
   \end{figure}

The excitation objectives are fixed on mounts which allow three dimensional translation plus pitch and yaw adjustment (LP-1A, Newport). In a first step the beam paths of both excitation arms where brought to overlap through irises placed on the breadboard and the optical bench without any microscope objectives. We found it useful to use two mirrors in each periscope, one vertically mounted and one mounted at $45\degree$ for vertical deflection of the incoming beam. In this way full beam steering can be achieved to realign the periscope before hitting the galvo scanner. After this initial alignment the first excitation objective was then placed into the beam path and brought to focus onto the sample mirror, which was adjusted to reflect the light back into the same objective. Using a shear plate and a beam splitter cube the back reflected light was qualitatively checked for collimation to ensure the sample mirror was correctly placed in the focal plane of the objective (Figure\ref{fig:alignment2},B). The sample mirror was then moved laterally to allow the excitation beam to pass through the drilled hole and the second excitation objective was placed (Figure\ref{fig:alignment2},C). This time collimation was checked with the light going through both objectives and so their confocal placement was insured. The microscope was then aligned recursively by starting at the putative confocal point between the objectives and placing successively lens after lens in the direction towards the light source. Finally, the sample mirror was position in reflection mode and the detection objective was aligned (Figure\ref{fig:alignment2},D).

\section{Optical characterisation}

@@

\begin{landscape}
\begin{table}[t!]
	\centering
		\caption[Optomechanics]{Overview of optomechanical components.\label{tab:optomechanics}}
		\begin{tabular}{llll}
		Component												&	Manufacturer															& Part\# 								& Specifications 																													\\\hline
		\multirow{5}{*}[2.5em]{Lasers} 	& \multirow{5}{*}[2.5em]{Cobolt AB, Sweden} & MLD										& 405nm (for DAPI), 80mW, s-polarised																					 \\
																		&																						& MLD										& 445nm (for CFP), 50mW, s-polarised																					 \\
																		&																						& Calypso 							& 491nm (for GFP, FITC), 50mW, s-polarised																		 \\
																		&																						& Fandango							& 515nm (for Venus, YFP), 50mW, s-polarised																		 \\
																		&																						& Jive									& 561nm (for dTomato, PI, RFP), 50mW, s-polarised															 \\
		AOFT 														& AA Opto-Electronic, France								& AOTFnC-400.650-TN 		&	\pbox[t]{10.5cm}{$>90\%$ diffraction efficiency, 3nm resolution, low cross talk between laser lines, high separation angle}\\
		Laser modulator 								& Qioptiq	GmbH, Germany											& LM 0202 VIS ADP				& 400-650nm , $\nicefrac{\lambda}{2}$-voltage (633nm): 210V										 \\
		Pulse amplifier 								& Falco Systems, The Netherlands						& WMA-300								& 50x amplification up to $\pm$ 150V, DC to 5MHz signal bandwidth							 \\
		Galvo scanner 									& Cambridge Technology, USA									& 6220H 								& small angle step response $200\mu s$																				 \\		
		\multirow{2}{*}[0.6em]{Objectives}&	Nikon; Japan														& Plan Fluor EPI 				& 10x0.3NA, WD 17.5mm, EFL 20mm (excitation)																	 \\
																		& Olympus, Japan														& LMPLFLN20X 						& 20x0.4NA, WD 12mm, EFL 9mm (detection)																			 \\
		\multirow{3}{*}[0.6em]{Motor stages}& \multirow{2}{*}[0.6em]{Physik Instrumente, Germany}& C-863.11	& DC servo-motor controller																										 \\
																		&																						&	M-122									& Travel range 25mm, $0.1\micro m$ resolution, max. velocity 20mm/s						\\
																		&																						& M-116 								& Precision Rotation Stage, $2.5\micro rad$, max. velocity $20\degree /s$ 		\\
		Camera 													& Hamamatsu, Japan													& Orca Flash4.0 				& \pbox[t]{10.5cm}{sCMOS sensor, 2048(H) x 2048(V), cell dim.: $6.5\micro m$, active area: 13.3mm x 13.3mm, 16bit images}\\
		DAQ board												& National Instruments, USA									& NI PCIe-6353					& \pbox[t]{10.5cm}{AI: 1 MS/s multichannel; 16-bit resolution, ±10 V; AO: 2.86 MS/s, 16-bit resolution, ±10 V; digital I/O lines (hardware-timed up to 10 MHz), 100MHz max counter frequency}\\
		Workstation											& Dell, USA																	& T7500									&  \pbox[t]{10.5cm}{12GB RAM, Intel Xeon Processor X5647 @ 2.93 GHz, 64bit OS, Win7}\\
		\end{tabular}
\end{table}
\end{landscape}

>>>>

Here we will present a state-of-the-art LSFM, as it is implemented in our lab, which is especially beneficial to acquire 3D data sets of large, clarified and structurally intact mouse brains. The LSFM features double-sided illumination with a digitally scanned light sheet and a sample chamber which has been specifically designed for the the imaging of large ($> 1cm^3$), immersed and freely movable samples. After briefly presenting the optical clearing protocol we employ to render our samples transparent, we explain how to prepare and mount the samples for stable, 3D imaging for several days. In addition to a detailed description of all opto-mechanical components, we further present a practical guide for the alignment of a LSFM, a non-trivial task whichhas too often been summarised in a single sentence. A systematic approach to handle, store and analyse the data is also given. We further explain about the data volume we produce how it can be reduced and handled. We finish with some nice data and an outlook.  The final sentence of the introduction needs to be amazing.

\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{PanelSampel.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:Panel0} (A) Schematic of light sheet microscopy. Excitation (blue) and fluorescence detection (green) occur on independent, perpendicular axes. (B) Mounting of a clarified, fluorescently labelled brain. The brain is glued onto a coverslip and inserted into an adapter that slides into a Teflon cylinder.} 
   \end{figure}

\section{Sample mounting}
%Biological tissue is, bar of very few exemptions like the cornea or zebrafish larvae, highly scattering. Scattering is the deflection of light rays due to the heterogeneous mixture of cells and sub-cellular structures with varying refractive indices. Rayleigh scattering, the nearly isotropic and strongly wavelength dependent scattering of light by particles much smaller than the wavelength of light, and Mie scattering, which occurs on cellular structures such as organelles and other refractive structures which are larger than the wavelength of light, far outweigh absorption and cause most biological tissues to be opaque. In the visible spectrum, the scattering of fluorescence photons is dominant over ballistic fluorescence such that for the imaging of large samples optical clearing methods based on refractive index matching have been employed. These methods involve several chemical sample preparation steps to generate transparent yet structurally and anatomically intact tissue.
%
%A successful optical clearing method not only renders the tissue transparent but also causes neither quenching of protein fluorescence nor tissue distortion and is compatible with repetitive immunostaining. A very promising method called CLARITY\cite{Chung2013,Tomer2014} transforms tissue into a nanoporous, hydrogel-hybridized, lipid-free form. Crucially for high through-put clearing and imaging of large samples, the protocol, however, is ideally also fast, easy and cheap. Our lab therefore development a versatile, simple, rapid and inexpensive clearing method based on a water-soluble agent, 2,2'-thiodiethanol (TDE) which in combination with CLARITY allows for the optical clearing of entire mouse brains or human biopsies. With this protocol (see [cite Irene] for a detailed description) a mouse brain (Figure\ref{fig:Panel1},B) takes 1 month to clear at a costs of \$XY.

\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{NuPanel1.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:Panel1} Schematic of light sheet microscopy. (A) Fluorescence excitation (along x axis) and detection (along z axis) are operated on independent, perpendicular light paths where the excitation light sheet and the detection focal plane overlap. The custom-made sample chamber is assembled with silicone bellows and seal rings. The clarified, fluorescently-labelled brain is mounted on a Teflon cylinder in the centre of the watertight chamber (C) and can be translated and rotated freely with piezo motors (D).} 
   \end{figure}

To elucidate neuronal projections and functional connections in structurally intact tissue it is paramount to be able to image centimeter-sized, clarified samples, such as mouse brains, with high resolution in whole mount preparation. While promising clearing protocols are well documented in literature\cite{Chung2013,Tomer2014}, the question of sample preparation and mounting in light sheet microscopy is not trivial but requires novel approaches to such extent that it is becoming a separate field of research and very diverse strategies such as FEP tubes, 3D printed chambers and Quartz cuvettes have been reported\cite{Kaufmann2012,Pitrone2013,Olarte2012,Tomer2014}, however, these approaches are limited to much smaller sample volumes. The problem of sample mounting in a light sheet microscope arises form the fact that optical access to the sample is required from 3-4 planar sides leaving only two opposing sides to insert, fix and move the sample. Most commonly the vertical direction is chosen. Stable mounting is hereby a key concern as a whole brain tomography can require image acquisition in excess of 24 hours and the effects of gravity, tissue shrinking/expansion and evaporation of the clearing solution over such time spans might have to be considered.

To acquire whole brain data sets, we fix a clarified and fluorescently-labelled mouse brain with super glue to a coverslip (Figure\ref{fig:Panel0},B). The brain is oriented along its axial orientation with the olfactory bulbs at the top and the cerebellum at the bottom of the coverslip. The coverslip is slid into a bottom adaptor and tightened with a plastic-capped grub screw. The bottom adaptor is inserted into a Teflon cylinder with the coverslip being positioned on the far side of the detection objective. Three different slits in the adapter correspond to varying distances to the detection objective and give variability in sample thickness for example to allow also for the mounting of rat brain hemispheres.

We designed a cubic, water-tight sample chamber (Figure\ref{fig:Panel1},A) that allows access from all six sides while maintaining the 3D integrity of large, clarified and fluorescently-labelled mouse brains. The sample chamber is tightly bolted  to the optical breadboard while soft connections using silicone bellows allow for adjustive movements of the objectives and free 3D motion of the motor stages (Figure\ref{fig:Panel1},B). All connections are sealed with rubber rings and silicone caulk and additionally tightened with cable binders. In this way the objectives can be refocused and realigned without compromising the watertight seal of the chamber (Figure\ref{fig:Panel1},C). The clarified brains are imaged immersed in clearing solution composed of 63\% TDE in Phosphate buffered saline (PBS) and a refractive index of 1.45. A motorized x-, y-, z-, $\theta$-stage (Physik Instrumente, see Table\ref{tab:optomechanics}) allows free 3D motion and rotation of the Teflon cylinder which reaches into the centre of the chamber (Figure\ref{fig:Panel1},D).

@@

The custom-made, confocal light sheet microscope is equipped with 5 linearly polarised, cw lasers for fluorescence excitation (Figure\ref{fig:excitation},A). The wavelengths were chosen to excite the most common fluorophores (see Table\ref{tab:optomechanics} for the manufacturer and specifications of opto-mechanical components). The laser light from each laser is first collimated and expanded with a telescope (f140, f200) and then combined into a common path with a beam steering mirror and a long-pass filter (Semrock, LaserMUX\texttrademark\ series). An acousto-optical tunable filter (AOTF) acts as fast ($\mu s$) electronically tunable filter which uses the acousto-optical interaction inside an anisotropic medium to select and transmit any combination of up to four of the laser lines. The radio-frequency applied on the AOTF transducer controls the wavelength being transmitted into the first order and the radio-frequency amplitude allows to adjust the transmitted light intensity. Due its nonlinear response we measured the AOTF light transmittance for each wavelength as a function of radio frequency amplitude and determined a look-up table to linearise the output. The zero order light is blocked by an iris. An electro-optical laser modulator acts like a wave plate with electronically controlled retardation and rapidly rotates (few hundreds ns) the input polarisation of the excitation light by $90\degree$. The wavelength-dependent, high voltage that needs to be applied to the birefringent crystal inside the modulator to change the optical path length is provided by a two-step pre-amplification system. First, a low voltage, analog signal from the DAQ board is pre-amplified with custom made electronics and then fed into a commercial high voltage amplifier. A digital line is used to electronically control the frequency with which the polarisation is changed. After the laser modulator the excitation beam is further expanded by a factor of two with two achromatic doublets (f100, f200).

From here on three different light paths can be chosen through flip mirrors. One light path option guides the light through an axicon (apex angle of $160\degree$) and an achromatic doublet (f50) to create a Bessel beam. The other two options create Gaussian beams of different beam diameter. This diameter variation translates to different fields of view later on in the detection path. The three options are recombined before a polarising beam splitter cube which splits the excitation light depending on its polarisation into one of the two identical excitation arms. The beam is reduced with a telescope (f350, f200) whose telecentric plane coincides with the mirrored surface of a galvanometric scanner (galvo). The galvos are mounted on a custom made optical breadboard which features two circular holes to pass the periscopic beams and a large central cut-out for the sample chamber and motor stages.

The scan mirror surface is re-imaged with a telescope (f50, f100) onto the back aperture of a long working distance, low magnification objective (Nikon, 10x 0.3NA WD 17.5mm). The two excitation objectives are designed for air immersion but are immersed into the clearing solution within the sample chamber. A coverslip glued to the front housing edge serves the dual purpose of maintaining the first diffractive surface between the front optical element and the air and to protect the front lens elements from the organic solvent. The light sheet is generated digitally\cite{Keller2008a,Keller2008b} by scanning the excitation beam across the focal plane of the detection objective. %This generates perfectly incoherent illumination resulting in fewer artefacts.%cite{StelzerNatMeth2014}.

@@

Fluorescence detection in light sheet microscopy is analogous to conventional wide-field microscopy. Fluorescence is collected with an objective that is specifically designed for immersion in clearing solutions. The objective is equipped with a correction collar allowing for immersion in media with refractive indices ranging from 1.41 to 1.52 (Olympus, XLSLPLN25XGMP). To image the whole volume of interest the objective has a relatively low magnification of 25x and a large working distance of 8mm yet a high numerical aperture (1.0NA) affords high resolution imaging. A tube lens of 200mm creates an image on a sCMOS camera (Orca Flash4.0, Hamamatsu) with a camera chip of over 4 megapixels. In contrast to CCD sensors each pixel of a sCMOS camera sensor has a separate photodetector and amplification unit which means that sCMOS pixels can be read out independently from each other. In the rolling shutter data acquisition mode only a subset of adjacent horizontal pixel lines is simultaneously exposed and this active detection region is moved across the image sensor. With the delay between the exposure of two adjacent lines set to the minimum time required to read out a single line ($9.7\micro s$, see Table\ref{tab:resolution}) the entire frame of 2048 horizontal lines is activated within 19.86ms. Setting the line exposure time to 3ms results in approx. 300 lines being simultaneously exposed. This detection area is swept from the top to the bottom of the chip and acts like a moving, virtual confocal slit corresponding to a width of $80\micro m$ in the sample space. With those values the camera acquires images at a frame rate of 44Hz. Synchronisation of the rolling shutter with the scanned illumination beam results in confocal line detection\cite{Baumgart2012}.

\section{Optical characterisation}
An overview of imaging properties and derived quantities is given in Table\ref{tab:resolution}.

	\subsection{Contrast}
	\subsection{Signal-to-noise ratio}
	\subsection{Optical sectioning}

\section{Alignment}

\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{Panel3.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:alignment} (A) Basic geometrical optics of a double-sided illumination light sheet microscope. AD: achromatic doublet, PBS: polarising beam splitter, red: objective back focal planes and conjugated telecentric planes, green: image planes, blue: 4f telecentric lens system, black: alignment irises. (B) Alignment mirror with drilled hole for light transmission, mount for tip adjustment and adaptor for the Teflon tube. (C) With lateral movement the alignment mirror can be placed such that light is transmitted into the opposing excitation arm. (D) The alignment mirror can be rotated to precisely reflect by $90\degree$.} 
   \end{figure}

For light sheet microscopy it is crucial that excitation and detection occur on perpendicular axes because any deviation from this geometry results in obscured images of reduced resolution and contrast. The objectives need to be perfectly confocal so that the fluorescence that is generated in the swept excitation beam also falls within the detection objective's focal plane. Telecentric imaging, that is the imaging with two lenses which are the sum of their focal lengths apart, a so-called 4f re-imaging system (Figure\ref{fig:alignment},A), is used to re-image the galvo scanners onto the back apertures of the excitation objectives. In the detection path, the camera chip needs to be positioned in an image plane of the detection objective. Additionally, homogeneous illumination from both sides impose strict symmetry considerations on both illumination arms that have not only to be sufficiently aligned within themselves respectively but function as a pair with recursive dependence.

Our microscope was aligned with two tools, a shear plate to qualitatively assess collimation and a small mirror that can be mounted inside the sample chamber where the sample would usually be. The 0.5in mirror was first pierced with a drill using a ceramic drill bit to produce a hole roughly in its centre of the approximately the same diameter as the excitation beam inside the sample chamber (Figure\ref{fig:alignment},B). Using a compact single axis adjustable mirror mount (V50-AX, Newport) attached to the Teflon cylinder inside the chamber allows to to adjust the pitch of the reflection with the mount and the yaw with the rotation stage while at the same time providing a very space efficient mounting for the pierced 0.5in mirror. With this ``sample mirror" three different position can be easily implemented, firstly, back reflection by hitting the reflective surface at $0\degree$, secondly, transmission by laterally displacing the mirror until the light passes through the drilled hole (Figure\ref{fig:alignment},C), and thirdly, reflection of the light by $90\degree$ by precisely turning the mirror mount by $45\degree$ using the rotation stage (Figure\ref{fig:alignment},D).

\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{Panel4.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:alignment2} (A) Working principle of a microscope objective (left): a collimated input beam is converted into a spherical wavefront. Right: inverted light path, a focal spot in the back aperture creates a collimated output. (B) Recursive placement of lenses using the sample mirror in back-reflection mode, (C) in transmission mode and (D) in reflection mode.} 
   \end{figure}

The excitation objectives are fixed on mounts which allow three dimensional translation plus pitch and yaw adjustment (LP-1A, Newport). In a first alignment step the beam paths of both excitation arms where brought to overlap through irises placed on the breadboard and the optical bench without any microscope objectives. We found it useful to use two mirrors in each periscope, one vertically mounted and one mounted at $45\degree$ for vertical deflection of the incoming beam. In this way full beam steering can be achieved to realign the periscope before hitting the galvo scanner. After this initial alignment the sample mirror was placed with its reflective surface in the centre of the central cut-out of the breadboard. The first excitation objective was placed into the beam path and brought to focus onto the sample mirror which was adjusted to reflect the light back into the same objective through the irises. Using a shear plate and a beam splitter cube the back reflected light was qualitatively adjusted for collimation using translation along the excitation axis of the objective mount (Figure\ref{fig:alignment2},B). The sample mirror was then moved laterally to allow the excitation beam to pass through the drilled hole and the second excitation objective was placed (Figure\ref{fig:alignment2},C). This time collimation was checked with the light going through both objectives and so their confocal placement was insured. Both excitation arms were then aligned recursively by starting at the putative confocal point between the objectives and placing successively lens after lens in the direction towards the light source, alternating between the two modalities illustrated in Figure\ref{fig:alignment2},A. Finally, the sample mirror was positioned in deflection mode and the detection objective was aligned (Figure\ref{fig:alignment2},D).

@@

\begin{landscape}
\begin{table}[t!]
	\centering
		\caption[Optomechanics]{Overview of optomechanical components.\label{tab:optomechanics}}
		\begin{tabular}{llll}
		Component												&	Manufacturer															& Part\# 								& Specifications 																											\\\hline
		\multirow{5}{*}[2.5em]{Lasers} 	& \multirow{5}{*}[2.5em]{Cobolt AB, Sweden} & MLD										& 405nm (for DAPI), 80mW, s-polarised																	\\
																		&																						& MLD										& 445nm (for CFP), 50mW, s-polarised																	\\
																		&																						& Calypso 							& 491nm (for GFP, FITC), 50mW, s-polarised														\\
																		&																						& Fandango							& 515nm (for Venus, YFP), 50mW, s-polarised														\\
																		&																						& Jive									& 561nm (for dTomato, PI, RFP), 50mW, s-polarised											\\\hline
		AOFT 														& AA Opto-Electronic, France								& AOTFnC-400.650-TN 		&	\pbox[t]{10.5cm}{$>90\%$ diffraction efficiency, 3nm resolution, low cross talk between laser lines, high separation angle}\\\hline
		Laser modulator 								& Qioptiq	GmbH, Germany											& LM 0202 VIS ADP				& 400-650nm , $\nicefrac{\lambda}{2}$-voltage (633nm): 210V						\\\hline
		Pulse amplifier 								& Falco Systems, The Netherlands						& WMA-300								& 50x amplification up to $\pm$ 150V, DC to 5MHz signal bandwidth			\\\hline
		Galvo scanner 									& Cambridge Technology, USA									& 6220H 								& small angle step response $200\mu s$																\\\hline		
		\multirow{2}{*}[0.6em]{Objectives}&	Nikon; Japan														& Plan Fluor EPI 				& 10x0.3NA, WD 17.5mm, EFL 20mm (excitation)													\\
																		& Olympus, Japan														& LMPLFLN20X 						& 20x0.4NA, WD 12mm, EFL 9mm (detection)															\\\hline
		\multirow{3}{*}[1.2em]{Motor stages}& \multirow{2}{*}[0.6em]{Physik Instrumente, Germany}& C-863.11	& DC servo-motor controller																						\\
																		&																						&	M-122									& Travel range 25mm, $0.1\micro m$ resolution, max. velocity 20mm/s		\\
																		&																						& M-116 								& Precision Rotation Stage, $2.5\micro rad$, max. velocity $20\degree /s$ \\\hline
		Camera 													& Hamamatsu, Japan													& Orca Flash4.0 				& \pbox[t]{10.5cm}{sCMOS sensor, 2048(H) x 2048(V), cell dim.: $6.5\micro m$, active area: 13.3mm x 13.3mm, 16bit images}\\\hline
		DAQ board												& National Instruments, USA									& NI PCIe-6353					& \pbox[t]{10.5cm}{AI: 1 MS/s multichannel; 16-bit resolution, ±10 V; AO: 2.86 MS/s, 16-bit resolution, ±10 V; digital I/O lines (hardware-timed up to 10 MHz), 100MHz max counter frequency}\\\hline
		Workstation											& Dell, USA																	& T7500									&  \pbox[t]{10.5cm}{12GB RAM, Intel Xeon Processor X5647 @ 2.93 GHz, 64bit OS, Win7}\\
		\end{tabular}
\end{table}
\end{landscape}
